Manuscript Code

### 2022-09-17 Manuscript Code.Rmd
Updating sensitivity analyses

coordinates(df_resids_locs) = ~longitude+latitude
# vario = variogram(resids_pnc~longitude+latitude, df_resids_locs)
# plot(vario)

@@

fig_4$variable <- recode(fig_4$variable, pnc_noscreen = "UFP (pt/cm3)", ma200_ir_bc1 = "BC (µg/m3)", no2 = "NO2 (ppb)", pm2.5_ug_m3 = "PM2.5 (µg/m3)", ) 
fig_4$race_eth_grp <- recode(fig_4$race_eth_grp, bk_p_ethn_non_hisp_white = "Non-Hispanic White", bk_p_race_asian = "Asian", bk_p_race_black = "Black", bk_p_ethn_hisp = "Hispanic")

@@

@@

## Assign A-D HOLC grades - Analysis 1
holc_grades$duplicated <- duplicated(holc_grades$BLOCKID10)
between_grades <- holc_grades[duplicated(holc_grades$BLOCKID10), ]$BLOCKID10
holc_no_dup <- holc_grades[!(holc_grades$BLOCKID10 %in% between_grades), ]

holc_no_dup$BLOCKID10 <- as.character(holc_no_dup$BLOCKID10)
redlining_blocks <- census_preds_wide %>%
  left_join(holc_no_dup, by=c("block_key"="BLOCKID10"))
redlining_blocks$count <- as.numeric(ave(redlining_blocks$block_key, redlining_blocks$block_key, FUN = length))

## Assign X HOLC grade - Analysis 1
redlining_blocks$holc_grade[is.na(redlining_blocks$holc_grade) & redlining_blocks$block_key %in% redlining_area$BLOCKID10] <- "X"
redlining_blocks <- na.omit(redlining_blocks)

## Assign A-D HOLC grades - Analysis 2
holc_areas <- read.csv("/projects/trap/transfer/kaya/area definition.csv")
holc_areas <- holc_areas[c("BLOCKID10", "holc_grade", "area")]
holc_area_per <- holc_areas %>%
    group_by(BLOCKID10) %>%
    mutate(percent = area/sum(area))

@@

## Assign X HOLC grade - Analysis 2
redlining_blocks_area$holc_grade[is.na(redlining_blocks_area$holc_grade) & redlining_blocks_area$block_key %in% redlining_area$BLOCKID10] <- "X"
redlining_blocks_area <- na.omit(redlining_blocks_area)

## Analysis 1: Pollution means weighted by block population divided by number of grades block is assigned to
redlining_blocks %>%
  group_by(holc_grade) %>%
  summarise(ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010/count),
            ufp_pct_diff = per_diff(ufp, 7102),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010/count),
            bc_pct_diff = per_diff(bc, 539),
            no2 = weighted.mean(no2, bk_tot_pop_2010/count),
            no2_pct_diff = per_diff(no2, 9.3),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010/count),
            pm2.5_pct_diff = per_diff(pm2.5, 4.7))

## Analysis 2: Pollution means weighted by block population divided by number of grades block is assigned to
redlining_blocks_area %>%
  group_by(holc_grade) %>%
  summarise(ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010*percent),
            ufp_pct_diff = per_diff(ufp, 7102),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010*percent),
            bc_pct_diff = per_diff(bc, 539),
            no2 = weighted.mean(no2, bk_tot_pop_2010*percent),
            no2_pct_diff = per_diff(no2, 9.3),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010*percent),
            pm2.5_pct_diff = per_diff(pm2.5, 4.7))

>>>>

coordinates(df_resids_locs) = ~longitude+latitude
vario = variogram(resids_pnc~longitude+latitude, df_resids_locs)
plot(vario)

@@

fig_4$variable <- recode(fig_4$variable, pnc_noscreen = "UFP (pt/cm3)", ma200_ir_bc1 = "BC (ng/m3)", no2 = "NO2 (ppb)", pm2.5_ug_m3 = "PM2.5 (µg/m3)", ) 
fig_4$race_eth_grp <- recode(fig_4$race_eth_grp, bk_p_ethn_non_hisp_white = "Non-Hispanic White", bk_p_race_asian = "Asian", bk_p_race_black = "Black", bk_p_ethn_hisp = "Hispanic")

@@

### Sensitivity Analysis: 2009-2013 Income Data

new_acs <- read.csv("/projects/trap/transfer/kaya/MANUSCRIPT DATA/merged_ACS.csv")
new_acs$new_income_group <- cut(new_acs$med_HH_inc_2019, c(0, 20000, 40000, 50000, 60000, 70000, 80000, 90000, 110000, 250001))
levels(new_acs$new_income_group) <- c("<$20k", "$20k-40k", "$40k-50k", "$50k-60k", "$60k-70k", "$70k-80k", "$80k-90k", "$90k-110k", ">$110k")
new_acs$blockgroup_key_2010 <- as.character(new_acs$blockgroup_key_2010)
new_census_preds_wide <- census_preds_wide %>%
  left_join(new_acs, by=c("blockgroup_key"="blockgroup_key_2010"))

new_census_preds_wide %>%
  group_by(new_income_group) %>%
  summarise(pop = sum(bk_tot_pop_2010),
            ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010),
            ufp_pct_diff = per_diff(ufp, 5584),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010),
            bc_pct_diff = per_diff(bc, 446.7),
            no2 = weighted.mean(no2, bk_tot_pop_2010),
            no2_pct_diff = per_diff(no2, 7.52),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010),
            pm2.5_pct_diff = per_diff(pm2.5, 4.259))

cor(new_census_preds_wide$bg_med_inc_hshld.x, new_census_preds_wide$med_HH_inc_2019)

@@

## Analysis 1: Only include blocks fully contained 
redlining_blocks_contained <- redlining_blocks[redlining_blocks$count == 1, ]

redlining_blocks_contained %>%
  group_by(holc_grade) %>%
  summarise(ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010),
            no2 = weighted.mean(no2, bk_tot_pop_2010),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010))

## Analysis 2: Pollution means weighted by block population divided proportionally to area
holc_areas <- read.csv("/projects/trap/transfer/kaya/area definition.csv")
holc_areas <- holc_areas[c("BLOCKID10", "holc_grade", "area")]
holc_area_per <- holc_areas %>%
    group_by(BLOCKID10) %>%
    mutate(percent = area/sum(area))

@@

redlining_blocks_area$holc_grade[is.na(redlining_blocks_area$holc_grade) & redlining_blocks_area$block_key %in% redlining_area$BLOCKID10] <- "X"
redlining_blocks_area <- na.omit(redlining_blocks_area)

redlining_blocks_area %>%
  group_by(holc_grade) %>%
  summarise(ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010*percent),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010*percent),
            no2 = weighted.mean(no2, bk_tot_pop_2010*percent),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010*percent))
